
#### Response Population 

```{r ageplot_response, echo=FALSE}
renderPlot({
  plot_response_agedist(dat = dpop())
})
```


```{r ageplot2_table, echo=FALSE}
tbl_resp_age <-  eventReactive(input$create, {
  table_response_agedist(dpop())
})
shiny::renderTable({tbl_resp_age()})
```



#### Table: Response Diagnoses

Response diagnoses includes following diagnoses on exposure group:

```{r selected_diagnoses_chunk2, echo = FALSE}
## TODO use response_diagnoses()
selected_diagnoses_response <- eventReactive(input$create, {
  table_summary_diagnoses(dpop(), response_diagnoses(), group = "response")
  ## TODO onko oikein. Pitaa olla koko data. & sama funktio exposurelle, tee vain yks funktio?
})

DT::dataTableOutput("tbl_selected_diagnoses2")
output$tbl_selected_diagnoses2 <- DT::renderDataTable( selected_diagnoses_response() , 
                                                       options = list(
                                                         # order = list(6, 'desc'),
                                                         rownames = F
                                                         
                                                       ))
```



#### First Diagnose Registry Source

Venn diagram shows how the exposure diagnose codes are found in different registries. In this plot only first diagnose per person is listed.

```{r, echo = FALSE}
renderPlot({
  venn_plot1(response_diagnoses())  
})

```


#### Venn diagram: Diagnoses Registry Overlap

Venn diagram shows how the exposure diagnose codes are found in different registries. In this plot only we can see in which registries we can find selected diagnoses per patient.

```{r, echo = FALSE}
renderPlot({
  venn_plot2(response_diagnoses())
})

```




#### Exposure & Response Cross Tabulation

```{r crosstab, echo = FALSE}
renderUI({
  HTML(  
    sjPlot::tab_xtab(var.row = dpop()$exposure, var.col = dpop()$response, title = "Population exposure and response diagnoses", show.row.prc = TRUE)$knitr
         )
})
```



#### Time difference

```{r echo=FALSE}
## Tän idea oli tehdä barplot, jossa on kuinka monta prosenttia exposure ennen responsee
tab_exp_resp <- reactive({
  d <- dpop() %>% 
     filter(exposure == 1 & response == 1) %>% 
  mutate(
    exp_resp = ifelse(DATE < resp.DATE, 1, ifelse(DATE == resp.DATE, 0, -1))
    # exp_resp = ifelse(exposure_date < response_date, 1, 0)
  ) %>% 
  group_by(exp_resp) %>% 
  summarise(
    n = n()
  ) %>% 
  mutate(
    percentage = round(100 * n / nrow(dpop() %>% filter(exposure == 1 & response == 1)), 1),
    exp_resp = factor(case_when(
      exp_resp == 1 ~ "Exposure < Response",
      exp_resp == 0 ~ "Exposure == Response",
      exp_resp == -1 ~ "Exposure > Response"
    ), levels = c("Exposure < Response", "Exposure == Response", "Exposure > Response"))
  )
  return(d)  
})

shiny::renderTable({tab_exp_resp()})
```

Diagnoses time difference (response - exposure)

```{r echo=FALSE}
d.boxplot <- reactive({
  dpop() %>% 
    filter(exposure == 1 & response == 1) %>% 
    mutate(
      categ = "Fun",
      date_diff = as.numeric(resp.DATE - DATE),
      date_diff2 = as.numeric((resp.DATE - DATE) / 365.25)
    ) %>% 
    select(categ, date_diff, date_diff2)
})

renderPlot({
  ggplot(d.boxplot()) +
    geom_boxplot(aes(x=categ, y=date_diff)) +
    labs(title = "Time difference in Days (response - exposure)",
         x="",
         y="Days")
})

renderPlot({
  ggplot(d.boxplot()) +
    geom_boxplot(aes(x=categ, y=date_diff2)) +
    labs(title = "Time difference in Years (response - exposure)",
         x="",
         y="Years")
})


d.boxplot.stats <- reactive({
  d1 <- d.boxplot() %>% 
    mutate(Stats = "Days") %>% 
    group_by(Stats) %>% 
    summarise(
      mean = round(mean(date_diff), 3),
      median = round(median(date_diff), 3),
      sd = round(sd(date_diff), 3),
      var = round(var(date_diff), 3),
      min = round(min(date_diff), 3),
      max = round(max(date_diff), 3)
    )
  
  d2 <- d.boxplot() %>% 
    mutate(Stats = "Years") %>% 
    group_by(Stats) %>% 
    summarise(
      mean = round(mean(date_diff2), 3),
      median = round(median(date_diff2), 3),
      sd = round(sd(date_diff2), 3),
      var = round(var(date_diff2), 3),
      min = round(min(date_diff2), 3),
      max = round(max(date_diff2), 3)
    )
  
  d <- d1 %>% rbind(d2)
  
  return(d)
})
shiny::renderTable({d.boxplot.stats()})
```

