
#### Exposure Population 

```{r exposure_age, echo=FALSE}
renderPlot({
  plot_exposure_agedist(dat = dpop())
})
tbl_exp_age <- eventReactive(input$create, {
  table_exposure_agedist(dpop())
})
shiny::renderTable({tbl_exp_age()})
```


#### Table: All Exposure Diagnoses

Exposure diagnoses includes following diagnoses. In this table all cases are listed (for example if same person has ICD-8, ICD-9 and ICD-10 diagnose, all those cases will be listed).

```{r selected_diagnoses_chunk, echo = FALSE}
selected_diagnoses_exposure <- eventReactive(input$create,{
  table_summary_diagnoses(dpop(), exposure_diagnoses(), group = "exposure")
})
DT::dataTableOutput("tbl_selected_diagnoses")
output$tbl_selected_diagnoses <- DT::renderDataTable( selected_diagnoses_exposure() , 
                                                      options = list(
                                                        # order = list(6, 'desc'),
                                                        rownames = F
                                                      ))
```


#### Venn: First Diagnose Registry Source

Venn diagram shows how the exposure diagnose codes are found in different registries. In this plot only first diagnose per person is listed.

```{r, echo = FALSE}
renderPlot({
  venn_plot1(exposure_diagnoses())  
})
```


#### Venn: Diagnoses Registry Overlap

Venn diagram shows how the exposure diagnose codes are found in different registries. In this plot only we can see in which registries we can find selected diagnoses per patient.

```{r, echo = FALSE}
renderPlot({
 venn_plot2(exposure_diagnoses())  
})
```
