
If option *removing cases before the exposure diagnose* is not selected, response diagnoses that occurred before exposure diagnose, are set to date 1. If you change the setting, you need to run results again.

```{r, echo = FALSE}
inputPanel(
  radioButtons(inputId = "newdiag_before", label = "Remove cases where response is before exposure diagnose:", choices = c(TRUE, FALSE), selected = FALSE)
)

dsurv <- eventReactive(input$create,{
  create_dsurv(dpop = dpop(), 
               data_response_diagnoses = response_diagnoses(), 
               censoring_date = as.Date("2023-12-21"), 
               newdiag_before = input$newdiag_before)
})

```



#### Kaplan-Meier

Survival analysis (Kaplan-Meier) tells how many will get the response diagnose after the exposure diagnose during the time.

```{r, echo = FALSE}
renderPlot({
  plot_kaplan_meier(dsurv = dsurv())
})
```


#### Competing Risk Analysis

Competing Risk analysis compares risk after the exposure diagnose to the death or response diagnose.

```{r, echo = FALSE}

renderPlot({
  plot_competing_risk(dsurv = dsurv())
})
```

